A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2025-01-06 manuscript/main.tex
Mon  6 Jan 2025 13:15:39 EST

\section{Abstract}
The rapid growth of quantum computing has seen a rise in the development of applicable near-term quantum algorithms. A promising candidate to run on current noisy intermediate-scale quantum (NISQ) hardware is quantum machine learning (QML). Parameterized quantum circuits can be learned as models in a hybrid classical-quantum approach. It has been shown that QML models may need less training data to generalize compared to classical methods. Although QML has been explored largely within classification tasks, regression tasks have received much less attention. Existing studies have only utilized few qubits and lack relevant practical applications. We will discuss our work on the development and comparisons of QML models for highly desired prediction of chemical properties such as bond dissociation energies and barrier height energies. Our work investigates the trainability, expressibility, and generalization capability of various quantum models for the purpose of regression of molecular properties. Our work also provides a benchmark against classical machine learning models and implications of using error mitigation techniques for QML. \par

>>>>

\section{Abstract}
Within the quantum machine learning (QML) field, parameterized quantum circuits (PQCs), built using fixed and parameterized gates, offer a hybrid approach for complex machine learning tasks. While many potential use cases have been proposed, the exploration of relevant datasets for chemists is lacking. Our study seeks to understand the possible advantages and disadvantages of PQCs for two chemically relevant datasets: one based on the bond separation energies of 49 different classes of bonds, called the BSE49 dataset, and another consisting of water confirmations, where coupled-cluster singles and doubles (CCSD) wave functions are predicted using electronic structure theory data from lower-level methods using the data-driven coupled-cluster (DDCC) method. In our study, we examine a combinatorial space of 14 data encoding layers and 12 variational (ansatz) layers, for a combined total of 168 PQCs. To calibrate our PQCs, we utilize a dataset of noisy linear, quadratic, and sine functions to explore the effects of the circuit width and depth, the effects of the feature set size, and various error mitigation techniques. Following this step, we similarly examine our chemically relevant datasets. Our work highlights the difficulties in encoding classical molecular representations in a PQC for predicting bond separation energies and the aptitude for PQCs for predicting molecular wave functions. \par
